Capstone Movielens Report

### 2025-05-17 reports/capstone-movielens.site/04.appendix.Rmd
RMD report updated: `data.plot` function description completed.

@@

::: { #func.mean_reg.params.param1 .sidebar }
  - **param1:** description;

:::
::: { #func.mean_reg.params.param2 .sidebar }
  - **param2:** description.

@@

::: { #func.data.plot.value .sidebar }
#### Value
\

@@

---------------------------------------------------------

@@

::: { #func.fname00.params.param1 .sidebar }
  - **param1:** description;

:::
::: { #func.fname00.params.param2 .sidebar }
  - **param2:** description.

@@

--------------------------------------------------------------------------------

@@

--------------------------------------------------------------------------------

--------------------------------------------------------------------------------

@@

--------------------------------------------------------------------------------

>>>>

Plots a graph based on the dataset passed in the [data](#func.mean_reg.params.data) parameter, using both points and a line.

@@

::: { #func.mean_reg.params.data .sidebar }
  - **data:** Dataset to use for the plot;

:::
::: { #func.mean_reg.params.title .sidebar }
  - **title:** Title of the plot;

:::
::: { #func.mean_reg.params.xname .sidebar }
  - **xname:** The name of the dataset column used as the source of the $x$ variable for the plot;

:::
::: { #func.mean_reg.params.yname .sidebar }
  - **yname:** The name of the dataset column used as the source of the $y$ variable for the plot;

:::
::: { #func.mean_reg.params.xlabel .sidebar }
  - *xlabel = NULL*:** The $x$ axis label. If `NULL`, the value of the `xname` parameter is used for the label;

:::
::: { #func.mean_reg.params.ylabel .sidebar }
  - **ylabel = NULL:** The $y$ axis label. If `NULL`, the value of the `yname` parameter is used for the label.;

:::
::: { #func.mean_reg.params. .sidebar }
  - **line_col = blue:** The line color;

:::
::: { #func.mean_reg.params. .sidebar }
  - **normalize = FALSE:** If `TRUE`, the deviation of $y$ from its mean is used to plot, rather than $y$ values. Otherwise, the value of $y$ is used.

@@

The function is a wrapper for the [ggplot2::ggplot](https://ggplot2.tidyverse.org/reference/ggplot.html) function and is a simple and convenient tool for visualizing the data of this project.

@@

### [data.helper.func0]() Function {#func.data.helper.func0}
\

::: { #func.data.helper.func0.Usage .sidebar }
#### Usage
\

::: { #func.data.helper.func0.params .sidebar }
#### Parameters
\

::: { #func.data.helper.func0.params.p1 .sidebar }
  - **p1:** description;

:::
::: { #func.data.helper.func0.params.2 .sidebar }
  - **p2:** description.

::: { #func.data.helper.func0.details .sidebar }
#### Details
\

::: { #func.data.helper.func0.value .sidebar }
#### Value
\

::: { #func.data.helper.func0.code .sidebar }
#### Source Code
\

The soure code of the [data.helper.func0]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the [data.helper.func0]() is also available in the [Some.Section]() section of the [Somefunctions.R]() script.
:::
:::

@@

::: { #func.fname00.params.p1 .sidebar }
  - **p1:** description;

:::
::: { #func.fname00.params.2 .sidebar }
  - **p2:** description.

@@

## Other Function Templates
\

@@

@@
